Supplementary appendix

### 2018-07-31 paper2_APPENDIX.Rmd
Add files via upload

1. Supplementary information about the images.

@@

3. Summary statistics.

4. Supplementary analyses.

5. English translation of the survey experiment.

@@

In this section, I provide additional details about the creation of the "real" and "fake" symbolic elements that were included in the policy plans in the survey.

@@

The campaign images which were included in the policy plans in the real symbols condition were downloaded from EPM's official website (http://www.sviva.gov.il), from the section that archives the Ministry's publications and public campaigns. After downloading the images, I cropped them (via GIMP software). The sources of the images are detailed below:

@@

The fake logo was created via MS paint software. I replaced the leaves/hands from the original logo with a shape of stars with rounded edges, and replaced the green color with blue. I deliberately selected a natural element - star - as opposed to an abstract geometric element, since marketing studies have pointed to the "naturalness" of logos, as one of the key aesthetic characteristics rendering logos more memorable and favorable [@henderson_1998].

To create the fake campaign images, I searched for photos of unfamiliar male models that resemble the look of the real endorsers, Tal Friedman and Ido Rosenblum, and their face expressions in the campaign images. For this purpose, I used the website www.istockphoto.com that offers multiple collections of professional images for purchase. The original photos which I purchased from the website, and their sources are detailed below. Thereafter, I took these images of models, and edited them (via GIMP software) to create images which are aesthetically similar to the original campaign images, yet without their symbolic aspects. For the recycling policy, I used the same image from EPM's reusable bags campaign, while replacing Rosenblum's face with the face of the unfamiliar model, and changing the color of the bag from green to blue. For the The Air-pollution policy, I took the purchased image of the unfamiliar model, and added a blue rectangle behind him (instead of the green background behind Friedman). I also added a blue geometric shape above the person's head, which I took from a logo of an Israeli mortgage bank, against Friedman's green hair. The latter addition was important, given that the green hair not only has a symbolic connotation, but also functions as an unusual, surprising element, that attracts people's attention.

@@

In this section, I report the results from two prior surveys, with regard to the recognizability, affect and associations of the "real" and "fake" symbolic elements, which were included in the policy plans in the survey. I conducted these examinations before conducting the experiment in order to validate my empirical assumptions with regard to comparison between the real and fake symbols. I assume that the real symbols are recognized, and that they evoke positive feelings and associations which are related to caring for the environment. By comparison, I assume that the fake symbols are not recognized, and are more neutral. They do not have a strong positive or negative affect, or strong specific associations.

@@

The first prior survey was conducted on May 2017 among `r SVIVA1_01 %>% nrow()` participants, which were recruited by iPanel. This survey was designed as a survey experiment, which was a first attempt to test the moderating role of personal relevance on the effects of symbols and information (but not the interaction between symbols and information). The experimental procedure had several methodological problems. Mainly, the assignment to experimental conditions yielded imbalanced groups, and the manipulations of symbolic elements and information was too subtle. Still, the survey included specific questions about the affect and symbolic associations of the logos and the colors, which provide valuable descriptive data. In this survey, the participants were assigned to one of three conditions of symbols: real symbols, fake symbols and no symbols. The real and fake symbols conditions included the same logos and colors which were eventually used in the final experiment (but not the campaign images). At the end of the survey, participants were asked about their familiarity with the logos and colors that appeared in their policy plans, and their affect. These items and their descriptive results are presented below.

@@

Overall, these results show that the real logo is relatively recognizable and has a fairly positive affect, whereas the fake logo is unrecognized and neutral. Participants were also asked "What is the first thought / association that comes to mind when you see the symbol?"  With regard to the real logo, many of the participants filled associations related to carting for the environment. Representative examples for such answers are: "environmental protection", "a desire to protect nature and the environment", "green policy", "together for the sake of nature", "connection between nature and man". The participants were similarly asked about the first thought / association that comes to their mind when they see the color. Representative answers for the green color were: "nature", "a green and healthy environment", "environment protection". The responses for the fake logo and the blue color were more diverse, and mostly unrelated to environmental issues.

@@

The second prior survey was conducted on January 2018 among `r CELEBS_00%>%nrow()` participants, which were similarly recruited via iPanel. This survey was designed as a pre-test that was aimed at assessing the recognizability, affect and associations of the real vs. fake campaign images. Participants were presented with the four campaign images (two real and two fake), in a random order. After every image, they were asked a series of questions regarding the familiarity and affect of the image and of the person presented. The items and their descriptive results are presented below.

@@

These results similarly show that the real campaign images are relatively recognizable and have a fairly positive affect, whereas the fake images and models are unrecognized and do not evoke strong negative of positive feelings. Finally, I similarly asked subjects to describe their first thoughts/associations regarding the images of Friedman and Rosenblum from their campaigns (without any text). Most of the participants associated Rosenblum's image to the reducing the use of disposable grocery bags, in line with the campaign's message (e.g. "reusable bag", "reusable instead of disposable bag for protecting the environment"). With regard to Friedman's grass-head image from his "starting to think green" campaign, participants mostly mentioned associations related to environmental awareness (e.g. "green head, thinking about the environment", "green environment", "think green"), and to the humoristic aspect (e.g. "funny", "comedian", "Funny advertisement", "hahaha").

@@

Below is the full text of the survey. Additional comments are presented in square beackets. The different experimental conditions of the two policy plans are included in the appendix of the main paper, and therefore were not included here. The original Qualtrics file is available upon request.

@@

**We are researchers from the Department of Political Science at the Hebrew University. The short questionnaire below is part of an academic study designed to teach us about the attitudes of Israeli citizens regarding environmental policy. Therefore, it is important for us that you answer the questionnaire seriously and honestly. The questionnaire filling time is about 5-10 minutes.**

**It is important for us to clarify that the questionnaire is voluntary. Filling out the questionnaire and submitting it represent your agreement to participate in the research. In addition, we wish to emphasize that the personal details of all the participants will remain confidential and that the data collected in the research will be used for research purposes only. Non-consent to participate will be expressed in not filling of the questionnaire. The questionnaire is phrased in masculine form [in Hebrew] but addresses both men and women.**

@@

7. I have great confidence/trust

@@

1. Little interested

@@

**Now, we would like to ask you a few general questions about your area of occupation.**

@@

3. Third Sector

@@

**What is your field of profession/study? ______________**

@@

**Compared to the current situation, do you think the government should assist more or less to promote your field of occupation?**

@@

**What, in your opinion, might attract people to choose your occupation? _________________________________________**

@@

**Next, we will present you two policy plans on specific environmental issues. The programs are taken from the publication of the "Work Plans for 2018" of the Ministry of Environmental Protection, which is published in the Ministry's website.**

**At the top of each policy plan presented the specific policy issue, followed by the main actions taken by the Ministry to promote the issue.**

[Participants are then presented with the two policy plans (air-pollution and recycling), in a random order. See description about the manipulations and the procedure in the main paper; Each policy plan is followed by the following questions]

**Now, we'd like to ask you a few questions about your position on the policy for "Reducing waste and increase recycling" / "Reducing the air-pollution in the Haifa-Bay":**

@@

**I believe that the actions mentioned in the policy plan will assist in fulfilling the policy goal**

@@

**I believe that the policy plan is in the interest of citizens**

@@

**I believe that EPM made an honest attempt to design a good policy plan**

@@

**I believe that the Ministry of Environmental Protection aims to keep its commitments in that policy plan.**

@@

**The following sentences describe the way in which you read the latest policy plan that regarded to "Reducing waste and increase recycling" / "Reducing the air-pollution in the Haifa-Bay".**

@@

**I paid much attention to reading the policy plan.**

@@

**I skimmed the actions in the policy plan.**

@@

**I tried to thoroughly understand the the policy plan.**

@@

**While going through the policy plan I was thinking about other things which are not related to it.**

@@

**Try recalling the content of the latest policy plan.**
[Each subjects was asked about the latest policy plan presenter to her]

@@

1. Supervision on the factories

@@

5. I can not remember

@@

1. Supervision on the manufacturers

2. compulsory charge on bags

@@

4. plastic bottles

5. I can not remember

@@

**When you see the image, what does it make you feel?**

1. Very negative feeling

@@

7. Very positive feeling

**The image is taken from an advertisement commercial of the Environmental Protection Ministry. To what extent to you remember the advertisement?**

@@

7. Very positive feeling

@@

7. Very positive feeling

**The image is taken from an advertisement commercial of the Environmental Protection Ministry. To what extent to you remember the advertisement?**

@@

**Thank you very much for participating in the study. Some of the policy programs presented to you during the questionnaire included content that was different from the original work plan or was presented differently. The tasks related to "raising awareness" and "reducing supervision" are invented tasks that are not part of the Ministry of Environmental Protection's policy. [For the fake symbols: In addition, the pictures of the people presented in the programs were not taken from the ministry's broadcasts, and their characters were used only for research purposes.]**

>>>>

1. Supplementary information about the images

@@

3. Summary statistics

4. Supplementary analyses

5. English translation of the survey experiment

@@

In this section, I provide additional details about how I created the "real" and "fake" symbolic elements that were included in the policy plans in the survey.

@@

The campaign images which were included in the policy plans in the "real symbols" condition were downloaded from EPM's official website (http://www.sviva.gov.il), from the section that archives the Ministry's publications and public campaigns. After downloading the images, I cropped them (using GIMP software). The sources of the images are detailed below:

@@

The fake logo and campaign images were specifically designed to represent graphical elements that resemble the look and aesthetic qualities of the real symbolic elements, as much as possible, while removing their symbolic aspects.
The fake logo was created using the MS paint software. I replaced the leaves/hands of the original logo, with stars with rounded edges, and replaced the green color with blue. I deliberately selected a natural element – a star - as opposed to an abstract geometric element, since marketing studies have pointed to the "naturalness" of logos, as one of the key aesthetic characteristics rendering logos more memorable and favorable [@henderson_1998].

To create the fake campaign images, I searched for photos of unfamiliar male models that resemble the look of the real endorsers, Tal Friedman and Ido Rosenblum, and their facial expressions in the campaign images. For this purpose, I used the website www.istockphoto.com where multiple collections of professional images can be purchased. The original photos which I purchased from the website, and their sources are detailed below. Thereafter, I took these images of models, and edited them (via GIMP software) to create images which are aesthetically similar to the original campaign images, yet without their symbolic aspects. For the recycling policy, I used the same image from EPM's reusable bags campaign, while replacing Rosenblum's face with the face of the unfamiliar model, and changing the color of the bag from green to blue. For the The Air-pollution policy, I took the purchased image of the unfamiliar model, and added a blue rectangle behind him (instead of the green background behind Friedman). I also added a blue geometric shape above the person's head, which I took from a logo of an Israeli mortgage bank, against Friedman's green hair. The latter addition was important, given that the green hair not only has a symbolic connotation, but also functions as an unusual, surprising element, that attracts people's attention.

@@

In this section, I report the results from two prior surveys, with regard to the recognizability, affect and associations of the "real" and "fake" symbolic elements, which were included in the policy plans in the survey. I conducted these examinations before conducting the experiment, in order to validate my empirical assumptions about comparing the real and fake symbols. I assume that the real symbols are recognized, and that they evoke positive feelings and associations which are related to caring for the environment. By comparison, I assume that the fake symbols are not recognized, and are more neutral. They do not have a strong positive or negative affect, or strong specific associations.

@@

The first prior survey was conducted on May 2017 among `r SVIVA1_01 %>% nrow()` participants, recruited using the internet panel company iPanel. This survey was designed as a survey experiment, which was a first attempt to test the moderating role of personal relevance on the effects of symbols and information (but not the interaction between symbols and information). The experimental procedure had several methodological problems. Mainly, the assignment to experimental conditions yielded imbalanced groups, and the manipulations of symbolic elements and information was too subtle. Still, the survey included specific questions about the affect and symbolic associations of the logos and the colors, which provide valuable descriptive data. In this survey, the participants were assigned to one of three conditions of symbols: real symbols, fake symbols and no symbols. The real and fake symbols conditions included the same logos and colors which were eventually used in the final experiment (but not the campaign images). At the end of the survey, participants were asked about their familiarity with the logos and colors that appeared in their policy plans, and their affect. These items and their descriptive results are presented below.

@@

Overall, these results show that the real logo is relatively recognizable and has a fairly positive affect, whereas the fake logo is unrecognized and neutral. Participants were also asked "What is the first thought / association that comes to mind when you see the symbol?" With regard to the real logo, many of the participants mentioned associations related to caring for the environment. Representative examples for such answers are: "environmental protection", "a desire to protect nature and the environment", "green policy", "together for the sake of nature", "connection between nature and man". The participants were similarly asked about the first thought / association that comes to their mind when they see the color. Representative answers for the green color were: "nature", "a green and healthy environment", "environmental protection". The responses for the fake logo and the blue color were more diverse, and mostly unrelated to environmental issues.

@@

The second prior survey was conducted in January 2018 among `r CELEBS_00%>%nrow()` participants, also recruited using iPanel. This survey was designed as a pre-test that was aimed at assessing the recognizability, affect and associations of the real vs. fake campaign images. Participants were presented with the four campaign images (two real and two fake), in random order. After every image, they were asked a series of questions regarding the familiarity and affect of the image and of the person presented. The items and their descriptive results are presented below.

@@

These results similarly show that the real campaign images are relatively recognizable and have a fairly positive affect, whereas the fake images and models are unrecognized and do not evoke strong negative or positive feelings. Finally, I also asked subjects to describe their first thoughts/associations regarding the images of Friedman and Rosenblum from their campaigns (without any text). Most of the participants associated Rosenblum's image to the reducing the use of disposable grocery bags, in line with the campaign's message (e.g. "reusable bag", "reusable instead of disposable bag for protecting the environment"). With regard to Friedman's grass-head image from his "starting to think green" campaign, participants mostly mentioned associations related to environmental awareness (e.g. "green head, thinking about the environment", "green environment", "think green"), and to the humoristic aspect (e.g. "funny", "comedian", "Funny advertisement", "hahaha").

@@

Below is the full text of the survey. Additional comments are presented in square brackets. The different experimental conditions of the two policy plans are included in the appendix of the main paper, and therefore were not included here. The original Qualtrics file is available upon request.

@@

**We are researchers from the Department of Political Science at the Hebrew University. The short questionnaire below is part of an academic study designed to teach us about the attitudes of Israeli citizens regarding environmental policy. Therefore, it is important for us that you answer the questionnaire seriously and honestly. You have around 5-10 minutes to complete the questionnaire.**

**It is important for us to clarify that the questionnaire is voluntary. Filling out the questionnaire and submitting it represents your agreement to participate in the research. In addition, we wish to emphasize that the personal details of all the participants will remain confidential and that the data collected in the research will be used for research purposes only. You can express non-consent to participate by not filling in the questionnaire. The questionnaire is phrased in masculine form [in Hebrew] but addresses both men and women.**

@@

7. I have full confidence/trust

@@

1. Hardly interested

@@

**Now, we would like to ask you a few general questions about your occupation.**

@@

3. 3.	Civic Sector

@@

**What is your profession/field of study? ______________**

@@

**Compared to the current situation, do you think the government should assist more, or less to promote your field of occupation?**

@@

**What, in your opinion, might attract others to choose your occupation? _________________________________________**

@@

**Next, we will present to you two policy plans on specific environmental issues. The policy plans are taken from the publication “Work Plans for 2018” of the Ministry of Environmental Protection, which can be downloaded from the Ministry’s website.**

**The specific policy issue is presented at the top of each policy plan, and is followed by the main actions taken by the Ministry to promote the issue.**

[Participants are then presented with the two policy plans (air-pollution and recycling), in random order. See description about the manipulations and the procedure in the main paper; Each policy plan is followed by the following questions]

**Now, we’d like to ask you a few questions about your position on the policy for “Reducing the air-pollution in the Haifa-Bay”:**

@@

**I believe that the actions mentioned in the policy plan will assist in fulfilling the policy goal.**

@@

**I believe that the policy plan is in the citizens’ interest.**

@@

@@

**I believe that EPM made an honest attempt to design a good policy plan.**

**I believe that the Ministry of Environmental Protection aims to keep its commitments as laid out in the policy plan.**

@@

**The following sentences describe the way in which you read the latest policy plan regarding “Reducing the air-pollution in the Haifa-Bay”.**

@@

**I paid full attention to reading the policy plan [I read the policy plan in depth].**

@@

**I only skimmed the actions in the policy plan.**

@@

**I tried to thoroughly understand the policy plan.**

@@

**While going through the policy plan I was distracted by unrelated thoughts.**

@@

**Try recalling the content of the latest policy plan.**
[Each subject was asked about the latest policy plan presented to her]

@@

1. Supervision of factories

@@

5. I cannot remember

@@

1. Supervision of manufacturers

2. compulsory charge on carrier bags

@@

4. Plastic bottles

5. I cannot remember

@@

**When you see the image, what feelings does it invoke?**

1. Very negative feelings

@@

7. Very positive feelings

@@

7. Very positive feelings

@@

7. Very positive feelings

**The image is taken from an advertisement of the Environmental Protection Ministry. To what extent do you remember the advertisement?**

@@

**Thank you very much for participating in the study. Some of the policy programs presented to you during the questionnaire included content that was different from the original work plan or was presented differently. The tasks related to “raising awareness” and “reducing supervision” are fictional tasks that are not part of the Ministry of Environmental Protection’s policy. [For the fake symbols: In addition, the pictures of the people presented in the programs were not taken from the ministry’s broadcasts, and their characters were used only for research purposes.]**
